
---
title: '18200409'
author: "Mohammad Farhan Pasha (18200409)"
date: "October 09, 2018"
output:
  html_document:
    df_print: paged
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Task : 1

##Question : 1

###Load the Dataset with name of the countries as row names


```{r}
example <- read.csv('C:/Users/Farhan Pasha/Desktop/TT/R/Assignment 1/EurostatCrime2015.csv', header = TRUE, row.names = 1)
example
```




##Question : 2

###What's the size and structure of this dataset

```{r}
object.size(example)
ncol(example) #Number of Columns
nrow(example) #Number of Rows
str(example) #Structure

```

##Question : 3 Part 1

###Apend new Column Sex.crime which gives the sum of Rape,Sexual.assault and Sexual.voilence
```{r}
example$Sex.crime <- example$Rape+example$Sexual.assault+example$Sexual.violence
example
```

##Question : 3 Part 2

###Remove 3 columns : Rape, Sexual.assault and Sexual.violence
```{r}
example <- subset(example,select = -c(Rape, Sexual.assault, Sexual.violence))
example
```



##Question : 4

###With new dataset obtained, list countries that containes missing data.


```{r}
example_new <- example[!complete.cases(example),]
rownames(example_new)
```



##Question : 5

###Remove Countries with missing Values

```{r}
example <- na.omit(example)
example
```

##Question : 6

###Size of new dataframe

```{r}
object.size(example)
ncol(example) #Number of Columns
nrow(example) #Number of Rows

```


#Task : 2 Part 1

##The most common Crime in Ireland in 2015


```{r}

example <- cbind(rownames(example), example)
colnames(example)[1:1] <- c("COL1") # Naming the first column as col1.


ire <- example[example$COL1 == "Ireland",]

max <- apply(ire[,2:6],1,max) #Store the max value

print("Most Common Crime in Ireland in 2015:")
print(colnames(ire)[which(ire==max, arr.ind=TRUE)][2]) #Locate the column of that max value
```

#Task : 2 Part 2

##The least common Crime in Ireland in 2015


```{r}

minimum <- apply(ire[,2:6],1,min)

colnames(ire)[which(ire==minimum, arr.ind=TRUE)][2]

ire1 <- subset(ire, select = -c(Intentional.homicide)) #As we got homicide in first min, remove the whole column and again fing minimum
minimum <- apply(ire1[,2:5],1,min)
colnames(ire1)[which(ire1==minimum, arr.ind=TRUE)][2]

ire2 <- subset(ire1, select = -c(Robbery))#Remove above both column then find minimum again.
minimum <- apply(ire2[,2:4],1,min)
colnames(ire2)[which(ire2==minimum, arr.ind=TRUE)][2]
```

#Task : 2 Part 3

##Which country has the highest record of offences

```{r}

test<-example  #Copy...Because it is going to get modified.


test$total_offences <-  test$Assault + test$Intentional.homicide + test$Robbery + test$Theft + test$Sex.crime


max_values_offences <- max(test$total_offences) # Find Max of all totals
max_values_offences 

answer <-rownames(test)[which(test$total_offences==max_values_offences, arr.ind=TRUE)][1]
answer



```
#Task : 3

##Outline your findings


```{r}

slice <- c(0,sum(ire$Assault),sum(ire$Intentional.homicide),sum(ire$Robbery),sum(ire$Theft),sum(ire$Sex.crime))
label <- colnames(ire)

percent <- round(slice/sum(slice)*100)
label <- paste(label, percent) 
label <- paste(label,"%",sep="") # ad % to labels 

pie(slice, labels = label,col=rainbow(length(label)), main="Figure 1 : Pie Chart for % wise distribution of crimes.")
```



```{r}
Theft <- example$Theft
barplot(Theft, xlab = "Figure 2 : Theft",names.arg = rownames(example), ylab="Occurence")
```



#Conclusion: 
## Figure 1 : Theft comprises 76% of the total Crimes.

##Figure 2 : Scandinavian Countries like Denmark, Sweden, Finland have seen the highest rate of Thefts in 2015


